Toward Resolved Simulations of Burning Fronts in Thermonuclear X-ray Bursts

### 2018-09-27 astronum_2018/astronum-xrb.tex
First draft of stuff on multiscale

All of the above developments still involve fully compressible
hydrodynamics, but multiscale methods where we couple different hydrodynamics
solvers together in a single simulation may ultimately be needed to model the full star while resolving the burning front. \MarginPar{Alice and Ian contribute here}

>>>>

All of the above developments still involve fully compressible
hydrodynamics, but multiscale methods~\cite{weinan2011principles} where we couple different hydrodynamics
solvers together in a single simulation may ultimately be needed to model the full star while resolving the burning front. \MarginPar{Alice and Ian contribute here}
Such techniques rely on it being possible to decompose the dynamics of the system
into two scales, e.g.~a short and a long lengthscale, and that the processes at each
scale do not interact with each other. In the context of X-ray bursts, one possibility for
multiscale modelling would be to model the large scale dynamics using a shallow water model
(like that of~\cite{SPIT_ETAL02}) to capture the effects of the Coriolis force, and use
a fully compressible model in the vicinity of the burning front to capture
the turbulent burning processes. Given that the computational costs of the 2d shallow water model
would be negligible compared to those of the compressible model, the overall cost of 
this multiscale model would be determined by the size of the compressible region only. This
approach would therefore allow us to capture dynamics across the full star
without sacrificing resolution of the flame.
